Through the eyes of the teacher

### 2021-02-03 paper_1/paper_1_supplement.Rmd
update paper 1

authornote: |
  The study was carried out with the permission of Ethics Committee of the University of Leipzig.

abstract: |
  This document is a supplement to the paper.

keywords          : "keywords"
wordcount         : "X"

@@

floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

(1) Classroom management
(2) Positive climate and motivation
(3) Clarity and structuredness
(4) Activation and support
(5) Presence: posture and gaze
(6) Presence: voice
(7) Presence: verbal and non-verbal intervention
(8) Natural behaviour

The table below provides an overview over the mean, min, max and standard deviation of all scales.

@@

The individual items of a scale were further represented in graphs.

@@

@@

(5) Presence: posture and gaze
```{r Presence: posture and gaze line plots, fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

### presence: posture and gaze 
# filter by parameter variable, i.e. create a subset for Presence: posture and gaze
ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
ppg.plot.sd <- ppg.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
ppg.plot<-ggplot(data = ppg.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = ppg.data, y = "value", x = NULL,
       title="Presence: posture and gaze" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
ppg.plot

(6) Presence: voice
```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

### Presence: voice 
# filter by parameter variable, i.e. create a subset for Presence: voice
pv.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
pv.plot.sd <- pv.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pv.plot<-ggplot(data = pv.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pv.data, y = "value", x = NULL,
       title="Presence: voice" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pv.plot

(7) Presence: verbal and non-verbal intervention
```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

### Presence: verbal and non-verbal intervention 
# filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
pvni.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to create error bars, we need to summarize the data in a separate data frame
pvni.plot.sd <- pvni.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# long plot
pvni.plot<-ggplot(data = pvni.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = pvni.data, y = "value", x = NULL,
       title="Presence: verbal and non-verbal intervention" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pvni.plot

(8) Natural behaviour
```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

### Natural behaviour 
# filter by parameter variable, i.e. create a subset for Natural behaviour
nb.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")

@@

In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}

@@

>>>>

authornote: |
  The study was carried out with the permission of the Ethics Committee of the University of Leipzig.

abstract: |
  This document is a supplement to the paper and shows first graphs findings from the pilot study.

keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
wordcount         : "1949"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf #bookdown::word_document2
---

@@

(1) Classroom management
(2) Positive climate and motivation
(3) Clarity and structuredness
(4) Activation and support
(5) Presence: posture/gaze
(6) Presence: voice
(7) Presence: verbal and non-verbal intervention
(8) Natural behaviour

The table at the end of the manuscript provides an overview over the mean, the range and standard deviation of all scales.

@@

\newpage
The individual items of a scale are further represented in graphs.

@@

```
\newpage

(ref:presenceposturegaze-caption) (5) Presence: posture/gaze

```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)

# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

# ### Presence: posture/gaze 
# 
# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# ppg.plot.sd <- ppg.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# ppg.plot<-ggplot(data = ppg.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = ppg.data, y = "value", x = NULL,
#        title="Presence: posture/gaze" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# ppg.plot

@@

(ref:presencevoice-caption) (6) Presence: voice

```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)

# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
# 
# ### Presence: voice 
# # filter by parameter variable, i.e. create a subset for Presence: voice
# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# pv.plot.sd <- pv.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# pv.plot<-ggplot(data = pv.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = pv.data, y = "value", x = NULL,
#        title="Presence: voice" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# pv.plot

```
\newpage

(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention

```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)

# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
# 
# ### Presence: verbal and non-verbal intervention 
# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
# 
# # value sometimes contained text before filtering, we have to convert the numbers to numeric
# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# 
# # to create error bars, we need to summarize the data in a separate data frame
# pvni.plot.sd <- pvni.data %>%
#   group_by(group, item.wordings, .drop=TRUE) %>%
#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # long plot
# pvni.plot<-ggplot(data = pvni.plot.sd,
#                   aes(x = item.wordings, y = mean,
#                       group = group, colour = group)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   facet_grid(~perspective)+
#   labs(data = pvni.data, y = "value", x = NULL,
#        title="Presence: verbal and non-verbal intervention" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5),
#         axis.text.y = element_text(size = 6))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# pvni.plot

```
\newpage
(8) Natural behaviour
```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}

### Natural behaviour 
# filter by parameter variable, i.e. create a subset for Natural behaviour
nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")

@@

```
\newpage
In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.

```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}

@@

### Eye-Tracking Data

#### Gaze relational index (GRI)

The GRI is a measure of visual expertise in information processing. This metric is calculated as the ratio of mean fixation duration to fixation count. The GRI is higher for novices than for experts. (@gegenfurtner2020gaze)

```{r GRItable, echo = FALSE}

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_02_glasses_fixation_metrics.tsv", dec=",", sep="\t", header=T)

# calculate GRI

# create a basic table (tibble) using tidyverse functions
et.quest.table <- et.raw.data %>%
  summarise("M Fixation Number" = round(mean(Number_of_whole_fixations), 2),
            "SE Fixation Number" = round(se(Number_of_whole_fixations), 2),
            "M Duration Fixation" = round(mean(Total_duration_of_whole_fixations)),
            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations))
            )

# format and insert table in manuscript
apa_table(
  et.quest.table,
  caption = "Number and Duration of fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

### Coding Data

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme has been developed for coding:

### 2021-02-03 paper_1/paper_1_supplement.tex
update paper 1

The study was carried out with the permission of Ethics Committee of the University of Leipzig.

@@

\abstract{
This document is a supplement to the paper.
}

@@

(ref:data\_collection-caption) Example for the set up during a mini-lesson

\textbackslash begin\{figure\}

\{\centering \includegraphics{./pictures/data_collection}

\}

\textbackslash caption\{(ref:data\_collection-caption)\}(\#fig:data collection)
\textbackslash end\{figure\}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
\item
  Positive climate and motivation
\item
  Clarity and structuredness
\item
  Activation and support
\item
  Presence: posture and gaze
\item
  Presence: voice
\item
  Presence: verbal and non-verbal intervention
\item
  Natural behaviour
\end{enumerate}

The table below provides an overview over the mean, min, max and standard deviation of all scales.

@@

The individual items of a scale were further represented in graphs.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  Classroom management
  \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
\item
  Activation and support
  \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
\item
  Presence: posture and gaze
  \includegraphics{paper_1_supplement_files/figure-latex/Presence: posture and gaze line plots-1.pdf}
\item
  Presence: voice
  \includegraphics{paper_1_supplement_files/figure-latex/Presence: voice line plots-1.pdf}
\item
  Presence: verbal and non-verbal intervention
  \includegraphics{paper_1_supplement_files/figure-latex/Presence: verbal and non-verbal intervention line plots-1.pdf}
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
\end{enumerate}

In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}

Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.

\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}

@@

@@

@@

>>>>

The study was carried out with the permission of the Ethics Committee of the University of Leipzig.

@@

\abstract{
This document is a supplement to the paper and shows first graphs findings from the pilot study.
}

@@

\begin{figure}

{\centering \includegraphics{./pictures/datacollection}

\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
\item
  Positive climate and motivation
\item
  Clarity and structuredness
\item
  Activation and support
\item
  Presence: posture/gaze
\item
  Presence: voice
\item
  Presence: verbal and non-verbal intervention
\item
  Natural behaviour
\end{enumerate}

The table at the end of the manuscript provides an overview over the mean, the range and standard deviation of all scales.

@@

The individual items of a scale are further represented in graphs.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
  \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
  \newpage
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
  \newpage
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
  \newpage
\item
  Activation and support
  \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
  \newpage
\end{enumerate}

\begin{figure}

{\centering \includegraphics{./pictures/presenceposturegaze}

\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
\end{figure}

\begin{figure}

{\centering \includegraphics{./pictures/presencevoice}

\caption{(6) Presence: voice}\label{fig:presencevoice}
\end{figure}
\newpage

\begin{figure}

{\centering \includegraphics{./pictures/presenceverbalnonverbalintervention}

\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
\end{figure}
\newpage

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
  \newpage
  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
\end{enumerate}

\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
\newpage
Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.

\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
\newpage

@@

\hypertarget{eye-tracking-data}{%
\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}}

\hypertarget{gaze-relational-index-gri}{%
\paragraph{Gaze relational index (GRI)}\label{gaze-relational-index-gri}}

The GRI is a measure of visual expertise in information processing. This metric is calculated as the ratio of mean fixation duration to fixation count. The GRI is higher for novices than for experts. (Gegenfurtner et al. (2020))

\caption{\label{tab:GRItable}Number and Duration of fixations}

\begin{tabular}{llll}
\toprule
M Fixation Number & \multicolumn{1}{c}{SE Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation}\\
\midrule
842.50 & 146.69 & 382,411.00 & 95,132.00\\
\bottomrule
\end{tabular}

\hypertarget{coding-data}{%
\subsubsection{Coding Data}\label{coding-data}}

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). Therefore, a coding scheme was

@@

\leavevmode\hypertarget{ref-gegenfurtner2020gaze}{}%
Gegenfurtner, A., Boucheix, J.-M., Gruber, H., Hauser, F., Lehtinen, E., \& Lowe, R. K. (2020). The gaze relational index as a measure of visual expertise. \emph{Journal of Expertise. East Lansing, Michigan: Michigan State University, 2020, Vol. 3, Iss. 1}.

@@

\leavevmode\hypertarget{ref-kuckartz2019analyzing}{}%
Kuckartz, U., \& Rädiker, S. (2019). \emph{Analyzing qualitative data with MAXQDA}. Springer.
